---
title: "mca"
author: "Eliana Grosof"
date: "8/10/2020"
output: ioslides_presentation
---

Code came from/modified from http://www.gastonsanchez.com/visually-enforced/how-to/2012/10/13/MCA-in-R/


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, echo = TRUE}
data = read.csv('survey_cleaner.csv', na.strings="Not applicable")
head(data)
```

```{r}
#drop age from analysis for now
df = subset(data, select = -c(X, Age) )
df

#make cats for later 
cats = apply(df, 2, function(x) nlevels(as.factor(x)))
cats
# apply MCA
mca1 = MCA(df, graph = FALSE)
# list of results
mca1

mca1$eig

mca1$var
```

```{r}
# data frame with variable coordinates
mca1_vars_df = data.frame(mca1$var$coord, Variable = rep(names(cats), cats))

# data frame with observation coordinates
mca1_obs_df = data.frame(mca1$ind$coord)

# plot of variable categories
ggplot(data=mca1_vars_df, 
       aes(x = Dim.1, y = Dim.2, label = rownames(mca1_vars_df))) +
  geom_hline(yintercept = 0, colour = "gray70") +
  geom_vline(xintercept = 0, colour = "gray70") +
  geom_text(aes(colour=Variable)) +
  ggtitle("MCA plot of variables using R package FactoMineR")
```

So it's messy af, but it seems like country, and maybe even state, might have something to do with the variance. 
But it's really, really spread out and each dimension appears to equally explain the data. 
What if I take out my dependent variable, treatment?
```{r}
#drop age from analysis for now
df = subset(data, select = -c(X, Age, treatment) )
#make cats for later 
cats = apply(df, 2, function(x) nlevels(as.factor(x)))
cats
# apply MCA
mca1 = MCA(df, graph = FALSE)
# list of results
mca1
mca1$eig

```

It literally doesn't change anything. Cool. Well, I should look into techniques for predicting stuff when there is no one clear predictor. Good to know.